---
title: "RWorksheet-6"
author: "Daisy Ann O. Pajarillo"
date: "2022-11-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r, vector = TRUE}
library(ggplot2)
library(dplyr)

data(mpg)

df <- as.data.frame(mpg)
df



```


1. How many columns are in mpg dataset? How about the number of rows? Show the
codes and its result.

```{r, vector = TRUE}
mpg_dataset <- glimpse(df)



```



2. Which manufacturer has the most models in this data set? Which model has the most
variations? 

  Answer:There are 11 columns and 234 rows in mpg dataset
  

```{r, vector = TRUE}
mf <- mpg_dataset %>% 
  group_by(manufacturer, model) %>% tally(sort = TRUE)
mf

```



a. Group the manufacturers and find the unique models. Copy the codes and result


```{r, vector = TRUE}
unique_model <- mpg_dataset %>% group_by(manufacturer, model) %>% distinct(model) %>% count()
unique_model

colnames(unique_model) <- c("Manufacturer","Model" ,"Counts")
unique_model

```


b. Graph the result by using plot() and ggplot(). Write the codes and its resul


```{r, vector = TRUE}
plot(unique_model)
ggplot(unique_model, aes(Manufacturer, Model)) + geom_point()
      
```


3. Same dataset will be used. You are going to show the relationship of the modeland
the manufacturer


  a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
  
  
```{r, vector = TRUE}
ggplot(df, aes(model, manufacturer)) + geom_point()

```


  b. For you, is it useful? If not, how could you modify the data to make it more
informative?


  Answer: For me it is not quite useful. I think it is much more easy to understand data and more informative if it use the bar graph with the use of legend and not the point
 
 
 
  
4. Using the pipe (%>%), group the model and get the number of cars per model. Show
codes and its result.
  
  
```{r, vector = TRUE}
car_per_model <- mpg_dataset %>% group_by(model) %>% count()
car_per_model


colnames(car_per_model) <- c("Model", "Counts")
car_per_model

```


a. Plot using the geom_bar() + coord_flip() just like what is shown below. Show
codes and its result


```{r, vector = TRUE}
qplot(model,data = df, 
      main = "Number of Cars per Model",
      xlab = "Model",
      ylab = "Number of Cars", geom = "bar", fill = manufacturer) + coord_flip()

```


b. Use only the top 20 observations. Show code and results.


```{r, vector = TRUE}
top20 <- car_per_model[1:20,] %>% top_n(2)
top20

ggplot(top20,aes(x = Model, y = Counts)) + geom_bar(stat = "Identity") +coord_flip()

```



5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic colour = engine displacement. Title should be
“Relationship between No. of Cylinders and Engine Displacement”.


  a. Show the codes and its result.
  
  
```{r, vector = TRUE}
ggplot(data = mpg_dataset , mapping = aes(x = displ, y = cyl, main = "Relationship between No of Cylinders and  Engine Displacement")) + geom_point(mapping=aes(colour = "engine displacement")) 

```


b. How would you describe its relationship?

        Answer: The scattered plot show where the engine displacement clustered


6. Get the total number of observations for drv - type of drive train (f = front-wheel drive,
r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 2seater, etc.).
Plot using the geom_tile() where the number of observations for class be used as a
fill for aesthetics.



  a. Show the codes and its result for the narrative in #6.
```{r, vector = TRUE}
ggplot(data = mpg_dataset, mapping = aes(x = drv, y = class)) +
  geom_tile(aes(fill=class))

```

b. Interpret the result.
  Answer: In this plot there are a lot of missing tiles maybe because of the unobserved class.


7. Discuss the difference between these codes. Its outputs for each are shown below.


    Answer:  As what I have notice the code 1 is not color blue even if you put the the  color blue while in the code 2 is correct and it show the blue color. The diffences between the 2 code is that the colour. The colour() must inside the parenthesis or belong inside the mapping() argument not in aes()



  • Code #1
```{r, vector = TRUE}
ggplot(data = mpg) +geom_point (mapping = aes(x = displ, y = hwy, colour = "blue"))
```

 Code #2
```{r, vector = TRUE}
ggplot(data = mpg) +geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")

```

8.Try to run the command ?mpg. What is the result of this command?

    a. Which variables from mpg dataset are categorical?
```{r, vector = TRUE}
con_varb <-?mpg
con_varb           
             
```

b. Which are continuous variables?

       Answer:  The list of the continuous variables in mpg are: displ, year, cyl, and cty.
       
c. Plot the relationship between displ (engine displacement) and hwy(highway miles
per gallon). Mapped it with a continuous variable you have identified in #5-b. What is its
result? Why it produced such output?   The output show the plot that contains of continuous variable from light to dark color blue.

```{r, vector = TRUE}
ggplot(mpg, aes(x = cty, y = hwy, colour = displ)) + geom_point()

```

9. Plot the relationship between displ (engine displacement) and hwy(highway miles
per gallon) using geom_point(). Add a trend line over the existing plot using
geom_smooth() with se = FALSE. Default method is “loess”.

```{r, vector = TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=class)) +
  geom_smooth(se = FALSE)
 
```


10. Using the relationship of displ and hwy, add a trend line over existing plot. Set the
se = FALSE to remove the confidence interval and method = lm to check for linear
modeling.

```{r, vector = TRUE}

ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = class)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm)      

```



