---
title: "Worksheet-3b in R"
author: "Daisy Ann O. Pajarillo"
date: "2022-11-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Create a data frame using the table below.

 a. Write the codes.

```{r, vector = TRUE}

Respondents <- (1:20)
Respondents
sex <- c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2)
sex

father_ocpt <- c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1)
father_ocpt

person_home <- c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6)
person_home


sibling <- c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2)
sibling

house <- c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)
house

A <- data.frame(Respondents,sex,father_ocpt,person_home,sibling,house)
A

```

b. Describe the data. Get the structure or the summary of the data

          It computes summary statistics of data including the mean, 
          median, and maximum.
```{r, vector = TRUE}
summary(A)

```

c. Is the mean number of siblings attending is 5?
        Answer: No

d. Extract the 1st two rows and then all the columns using the subsetting functions.
Write the codes and its output.
```{r, vector = TRUE}
r <- subset(A[1:2, 1:6, drop= FALSE])
r
```

e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its
result

```{r, vector = TRUE}
r2 <- subset(A[c(3,5), c(2,4)])
r2
```

f. Select the variable types of houses then store the vector that results as types_houses.
Write the codes.
```{r, vector = TRUE}
r3 <- subset(A[c(1:20), c(2,6)])
r3

```
g. Select only all Males respondent that their father occupation was farmer. Write
the codes and its output.
```{r, vector = TRUE}
sel <- subset(A[c(1:20), c(2,3)] )
sel
Male <- sel[A$father_ocpt=='1',]
Male

```

h. Select only all females respondent that have greater than or equal to 5 number
of siblings attending school. Write the codes and its outputs.
```{r, vector = TRUE}
sel2 <- subset(A[c(1:20), c(2,5)])
sel2
Female <- sel2[A$sibling>='5',]
Female

```

2. Write a R program to create an empty data frame. Using the following codes:
```{r, vector = TRUE}
df = data.frame(Ints=integer(),

Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
print(str(df))
```
a. Describe the results.

       It give information of the class of the object.


3. Interpret the graph

Answer: The graph represents that people's negative sentiments each day towards Donald Trump from the date July 14, 2021 to July 21, 2021 are higher than positive and neutral




