---
title: "Project-2"
author: "Daisy Ann Pajarillo"
date: "2022-12-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Extract 10000 tweets from Twitter using twitteR package including retweets.
Subset the retweets and the original tweets into a separate file
Plot the retweets and the original tweets using bar graph in vertical manner.
Include legends



install library
```{r, vector = TRUE}
install.packages("twitteR")
install.packages("tm")
install.packages("tidytext")
install.packages("ggplot2")
install.packages("plotly")
install.packages("RColorBrewer")
install.packages("dplyr")
install.packages("wordcloud")
install.packages("wordcloud2")
install.packages("tidyr")
library(twitteR)
library(tm)
library(tidytext)
library(ggplot2)
library(plotly)
library(RColorBrewer)
library(dplyr)
library(wordcloud)
library(wordcloud2)
library(tidyr)
library(base64enc)
library(httr)
library(httr2)
```


setup credentials
```{r, vector = TRUE}
 CONSUMER_KEY <- "DcdqJsM1Ofn5Fqh6ScRe09h1Y"
CONSUMER_SECRET <- "BhRCZ0sR0tIcAtCsMTo30FRMElZvi9mOR5ItaprKbLSWthDbqI"
ACCESS_TOKEN <- "1594988417439305728-uYsYMoXYpMON9nk7qv89xiK9OQ2Gzi"
ACCESS_SECRET <- "Qy2ngnEOvhzXJHiy587E0jZkHveHohdSodad3g5YdWzkT"

```



```{r, vector = TRUE}

setup_twitter_oauth(consumer_secret = CONSUMER_SECRET,
                   consumer_key = CONSUMER_KEY,
                 access_token = ACCESS_TOKEN,
                 access_secret = ACCESS_SECRET)
                  


```
Extract tweets
```{r, vector = TRUE}

tweets <- searchTwitter("kpop", 
                             n = 10000,
                             lang = "en",
                             since = "2022-11-27",
                             until = "2022-12-10",
                             retryOnRateLimit=120)


tweets


```


Covert Data to data frame. 
Save and load data file
```{r, vector = TRUE}

tweetsDF<- twListToDF(tweets)

save(tweetsDF, file = "tweetsDF.Rdata")
load(file = "tweetsDF.Rdata")


```

Checking for missing values in a data frame
```{r, vector = TRUE}
missingValue <-sapply(tweetsDF, function(x) sum(is.na(x)))

missingValue
```


Subsetting using the dplyr()package
 Save and load the data file
```{r, vector = TRUE}
twts<- tweetsDF %>%
  select(screenName,text,created, isRetweet) %>% filter(isRetweet == FALSE)

twts



save(twts, file = "twts.Rdata")
load(file = "twts.Rdata")


```


Grouping the date created
```{r, vector = TRUE}

twts %>%  group_by(1) %>%  summarise(max = max(created), min = min(created))


```


Getting the min and max
```{r, vector = TRUE}

twts <- twts %>%  mutate(Created_At_Round = created %>% round
                         (units = 'hours') %>%as.POSIXct())


mintwts <- twts %>% pull(created) %>% min()
mintwts
 
maxtwts <- twts %>% pull(created) %>% max()
maxtwts


```


Using plotly() package and ggplot()
```{r, vector = TRUE}

twtsPlot <- ggplot(twts, aes(x = Created_At_Round)) +
  geom_histogram(aes(fill = ..count..)) +theme(legend.position = "left") +
  xlab("Time") + ylab("Number of tweets") + 
  scale_fill_gradient() 

twtsPlot %>% ggplotly()





```



Retweet Data
```{r, vector = TRUE}

retwt <- tweetsDF %>%
  select(screenName,text,created, isRetweet) %>% filter(isRetweet == TRUE)

```


Grouping the data created in Retweet
```{r, vector = TRUE}
retwt %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))


```


Getting min and max 
```{r, vector = TRUE}

retwts1 <- retwt %>%  mutate(Created_At_Round = created %>% round
                         (units = 'hours') %>%as.POSIXct())


min_retwts <- retwts %>% pull(created) %>% min()
min_retwts
 
max_retwts <- retwts %>% pull(created) %>% max()
max_retwts





```

Plotting Retweets Using plotly() package and ggplot()
```{r, vector = TRUE}

retwtPlot <- ggplot(retwts1, aes(x = Created_At_Round)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "left") +
  xlab("Time") + ylab("Number of tweets") + 
  scale_fill_gradient()

retwtPlot %>% ggplotly()


 

```


