---
title: "Worksheet-4"
author: "Daisy Ann Pajarillo"
date: "2022-11-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The table below shows the data about shoe size and height. Create a data frame..
```{r, vector = TRUE}
Shoesize <- c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0)
Shoesize

Height <- c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0)
Height

Gender <- c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")
Gender



data1 <- data.frame(Shoesize, Height, Gender)
data1

```
a. Describe the data.
    Yes, there is a relationship that exists between shoe size and height. Short people have a smaller shoe size while taller people have a larger shoe size.


b. Find the mean of shoe size and height of the respondents.
Copy the codes and results.
```{r, vector = TRUE}
respondent_shoesize <- mean(Shoesize)
respondent_shoesize

respondent_Height <- mean(Height)
respondent_Height



```
c. Is there a relationship between shoe size and height? Why?
    Yes there are relationship between shoe size and height because people with large     shoe sizes are usually tall but it differs if the person is male or                  female. The male usually has a larger size of shoes because they are                 taller than female




2. Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.
Consider data consisting of the names of months:
```{r, vector = TRUE}
Month <- c("March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August",
"July","December","August","August","September","November","February","April"
)
Month


factor_month_vector <- factor(Month)
factor_month_vector
```

3. Then check the summary() of the months_vector and factor_months_vector. |
Interpret the results of both vectors. Are they both equally useful in this case?

```{r, vector = TRUE}
summary1 <-summary(Month)
summary1

summary2 <- summary(factor_month_vector)
summary2
```
 Are they both equally useful in this case?
    Yes because you can see how many data or months have been repeated
    
    
4. Create a vector and factor for the table below.
```{r, vector = TRUE}
a <- c("East"= '1', "West"= '4', "North" = '3')
a

new_order_data <- factor(a,levels = c("East","West","North"))
print(new_order_data)



```

5. Enter the data below in Excel with file name = import_march.csv
  a. Import the excel file into the Environment Pane using read.table() function.
    Write the code
```{r, vector = TRUE}
getwd()
import_data <- read.table("/cloud/project/pajarillo_repo/Rworksheet-3b-4-5/Rworksheet-4/import_march.csv", header = TRUE, sep=",")
import_data
 

```


b. View the dataset. Write the code and its result.

```{vector = TRUE}
View(import_data)


```
