---
title: "Rworksheet-5"
author: "Daisy Ann O. Pajarillo"
date: "2022-11-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The table shows the enrollment of BS in Computer Science, SY 2010-2011

```{r, vector = TRUE}

BS <- data.frame("Course Year" = c ("1st", "2nd", "3rd", "4th"), "2019–2020" = c(80, 75, 70, 60))
BS

```

a. Plot the data using a bar graph. Write the codes and copy the result.

```{r, vector = TRUE}
bar <- c("1st" = 80, "2nd" = 75, "3rd" = 70, "4th" = 60)
bar
barplot(bar)

```

b. Using the same table, label the barchart with Title = ” Enrollment of BS Computer Science" horizontal axis = “Curriculum Year” and vertical axis = “number of students”

```{r, vector = TRUE}

bar <- c("1st" = 80 , "2nd" = 75, "3rd" = 70, "4th" = 60)
bar
barplot(bar,  main = "Enrollment of BS Computer Science",  xlab = "Number of Students",  ylab = "Course Year")

```

2. The monthly income of De Jesus family was spent on the following: 60% on Food, 10% on electricity, 5% for savings, and 25% for other miscellaneous expenses.

    a. Create a table for the above scenario. Write the codes and its result.
```{r, vector = TRUE}

Monthly <- data.frame(facts = c("Food", "Electricity", "Savings", "Miscellaneous_expenses"), A = c(60, 10, 5, 25))
Monthly
Tab1 <- table(Monthly)
Tab1

```

b. Plot the data using a pie chart. Add labels, colors and legend. Write the codes and its result

```{r, vector = TRUE}
A <- c(60, 10, 50, 25)
A
data1 <- round(A/sum(A) * 100, 1)
data1
data1 <- paste(data1,"%",sep = "")
data1
pie1 <- pie(A, main = "Month Data", col = rainbow(4),
              labels =  data1, cex = 0.8)

legend(1.3,1.5, c("Food","Electricity","Savings","Miscellaneous expenses"), cex = 0.8,fill = rainbow(4))

```

3. Open the mtcars dataset.

      a. Create a simple histogram specifically for mpg (miles per gallon) variable.           Use $ to select the mpg only. Write the codes and its result.
```{r, vector = TRUE}

data("mtcars")
datamtcars <- (mtcars$mpg)
datamtcars
hist(datamtcars, breaks = 12)

```

b. Colored histogram with different number of bins. #Note: breaks= controls the number of bins.

```{r, vector = TRUE}

hist(mtcars$mpg, breaks=12, col="yellow")
hist(datamtcars, breaks=12, col="cyan")

```

c. Add a Normal Curve

```{r, vector = TRUE}

x <- mtcars$mpg
h<-hist(x, breaks=10, col="red", xlab="Miles Per Gallon",
        main="Histogram with Normal Curve")
xfit<-seq(min(x),max(x),length=40)
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=2)

curv <- datamtcars
curv

hist1 <-hist(curv, breaks=10, col="red", xlab="Miles Per Gallon",
                 main="Histogram with Normal Curve")
xfit<-seq(min(curv),max(curv),length=40)
yfit<-dnorm(xfit,mean=mean(curv),sd=sd(curv))
yfit <- yfit*diff(hist1$mids[1:2])*length(curv)
lines(xfit, yfit, col="blue", lwd=2)
hist1

```

4. Open the iris dataset. Create a subset for each species

    a. Write the codes and its result.

```{r, vector = TRUE}

data("iris")
data_iris <- data.frame(iris)
data_iris

seto <- subset(data_iris, Species == 'setosa' )
seto

versi <- subset(data_iris, Species == 'versicolor' )
versi

virg <- subset(data_iris, Species == 'virginica' )
virg

```

b. Get the mean for every characteristics of each species using colMeans().
    Write the codes and its result.
    Example: setosa <- colMeans(setosa[sapply(setosaDF,is.numeric)])
```{r, vector = TRUE}

setosa <- colMeans(seto[sapply(seto,is.numeric)])
setosa

versicolor <- colMeans(versi[sapply(versi,is.numeric)])
versicolor

virginica <- colMeans(virg[sapply(virg,is.numeric)])
virginica

```

c. Combine all species by using rbind() The table should be look like this:

```{r, vector = TRUE}

combine_species <- rbind(c(setosa, versicolor,virginica))
combine_species

combine_data<- data.frame(combine_species)
combine_data

```

d From the data in 4-c: Create the barplot().
    Write the codes and its result.
    The barplot should be like this.
```{r, vector = TRUE}

barplot(as.matrix(combine_species), beside = TRUE,
        main = "Iris Data",
        xlab = "Characteristics",
        ylab = "Mean Scores",
        col = c("red", "green", "blue"))

```

